---
title: "Simulation to assess varying coefficients and guideline"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

This runs a small simulation where we have varying beta_theta over time.
We actually conduct the matching analysis and compare it to the empirical to see how our guideline works when it is technically misspecified. 

In particular, this document produces Figure 4 and Table 2 in Appendix B. 


## Make data 
```{r}
# this will only make data for the specific set up with (X, Z, theta)
# extends your make data function to account for Z
#
# rho: correlation of Xs with theta.
make_data = function(N,
                     beta_theta_1, beta_theta_0, beta_theta_pre,
                     beta_X_1, beta_X_0, beta_X_pre, 
                     beta_Z_1, beta_Z_0, beta_Z_pre, 
                     mu_theta_1, mu_theta_0,
                     mu_X_1, mu_X_0,
                     mu_Z_1, mu_Z_0,
                     sigma2_theta = 1, sigma2_X = 1, sigma2_Z = 1,
                     sigma2_pre = 1.3, sigma2_post = sigma2_pre,
                     p = 0.2, num_pre = 2, rho = c(0.3, 0.4), a, seed = NULL) {
    
    sigma_theta = sqrt(sigma2_theta)
    sigma_X = sqrt(sigma2_X)
    sigma_pre = sqrt(sigma2_pre)
    sigma_post = sqrt(sigma2_post)
    sigma_Z = sqrt(sigma2_Z)
    
    stopifnot( num_pre >= 1 )
    
    if ( !is.null(seed) ) {
        set.seed(seed)
    }
    
    treatment = sample(c(0, 1), size = N, replace = TRUE, prob = c(1-p, p))
    mu_1 = c(mu_theta_1, mu_X_1, mu_Z_1)
    mu_0 = c(mu_theta_0, mu_X_0, mu_Z_0)
    
    sigma_XX <- matrix(c(sig_x^2, a, a, sig_z^2),
                       2)
    sigma_thetaXZ = matrix(c(sigma_theta^2, sigma_theta*sigma_X*rho[1], sigma_theta*sigma_Z*rho[2],
                             sigma_theta*sigma_X*rho[1], sigma_X^2, a,
                             sigma_theta*sigma_Z*rho[2], a, sigma_Z^2), byrow = TRUE, nrow = 3)
    
    treats = mvrnorm(sum(treatment == 1), mu_1, sigma_thetaXZ)
    controls = mvrnorm(sum(treatment == 0), mu_0, sigma_thetaXZ)
    
    theta = rep(NA, N)
    X = rep(NA, N)
    Z = rep(NA, N)
    
    theta[treatment == 1] = treats[, 1]
    theta[treatment == 0] = controls[, 1]
    X[treatment == 1] = treats[, 2]
    X[treatment == 0] = controls[, 2]
    Z[treatment == 1] = treats[, 3]
    Z[treatment == 0] = controls[, 3]
    
    Y_pre = list()
    Y_post = 5 + beta_theta_1*theta + beta_X_1*X + beta_Z_1*Z + rnorm(N, mean = 0, sd = sigma_post)
    Y_0 = 2 + beta_theta_0*theta + beta_X_0*X + beta_Z_0*Z + rnorm(N, mean = 0, sd = sigma_pre)
    Y_pre = 1 + beta_theta_pre*theta + beta_X_pre*X + beta_Z_pre*Z + rnorm(N, mean = 0, sd = sigma_pre)
    
    df = data.frame(treatment = treatment, theta, X, Z, Y_pre, Y_0, Y_post)
    
    return(df)
}

```

## I will now basically make the oracle_bias calculator redefined to account for Z but for this special setting
```{r}
library(dplyr)
library(MASS)



# I will not use the oracle_bias calculator instead assume specifically T = 2, with (X, Z) covariates
# and any arbitary correlations within all (X, Z, \theta)

# the following functions manually calculate the bias (note this only works for T = 2)
# two covariate (X, Z) and one univariate theta that might have different correlation rho (2 dimensional)
# two time periods that I will break Assumption 1 or not
# e.g. rho = c(0.3, 0.5) means the cor(X, theta) = 0.3, cor(Z, theta) = 0.5
# input a also characterizes the covariance between X and Z, i.e., cov(X, Z) = a 
# input: beta_theta_0 is T = 1, beta_theta_pre is T = 0, and beta_theta_1 is T = 2. I'm sorry for this confusing definition. 

bias_match_both_truth = function(rho, beta_theta_0, beta_x_0, beta_theta_1, beta_x_1, beta_z_1, beta_z_0,
                                 beta_theta_pre, beta_x_pre, beta_z_pre,
                                 mu_theta_1, mu_theta_0, mu_x_1, mu_x_0,  mu_z_1, mu_z_0, sig_theta,
                                 sig_x, sig_z, sigma_pre, a = 0) {
    # cov matrix of X
    sigma_XX <- matrix(c(sig_x^2, a, a, sig_z^2),
                       2)
    # cov matrix of theta and X
    sigma_thetax = matrix(c(sig_theta*sig_x*rho[1], sig_theta*sig_z*rho[2]), nrow = 1)
    # cov matrix of theta and 2 pre-period outcomes (that are identically distributed under perfect parallel trends)
    
    sigma_thetay = matrix(c(beta_theta_0*sig_theta^2 + beta_x_0*sig_x*rho[1]*sig_theta + beta_z_0*sig_z*rho[2]*sig_theta, beta_theta_pre*sig_theta^2 + beta_x_pre*sig_x*rho[1]*sig_theta + beta_z_pre*sig_z*rho[2]*sig_theta), nrow = 1)
    # cov matrix of X and 2 pre-period outcomes
    sigma_xy = matrix(c(beta_x_0*sig_x^2 + beta_theta_0*rho[1]*sig_theta*sig_x + beta_z_0*a,
                        beta_x_pre*sig_x^2 + beta_theta_pre*rho[1]*sig_theta*sig_x + beta_z_pre*a,
                        beta_z_0*sig_z^2 + beta_theta_0*rho[2]*sig_theta*sig_z + beta_x_0*a,
                        beta_z_pre*sig_z^2 + beta_theta_pre*rho[2]*sig_theta*sig_z + beta_x_pre*a), 2, byrow = TRUE)
    
    vec_beta_x_0 = matrix(c(beta_x_0, beta_z_0), ncol = 1)
    vec_beta_x_pre = matrix(c(beta_x_pre, beta_z_pre), ncol = 1)
    # total variance of Y_pre
    d = beta_theta_0^2*sig_theta^2 + beta_x_0^2*sig_x^2 + beta_z_0^2*sig_z^2 + 2*beta_theta_0*beta_x_0*rho[1]*sig_theta*sig_x +
        2*beta_theta_0*beta_z_0*sig_theta*sig_z*rho[2] + 2*beta_z_0*beta_x_0*a + sigma_pre^2
    d2 = beta_theta_pre^2*sig_theta^2 + beta_x_pre^2*sig_x^2 + beta_z_pre^2*sig_z^2 + 2*beta_theta_pre*beta_x_pre*rho[1]*sig_theta*sig_x +
        2*beta_theta_pre*beta_z_pre*sig_theta*sig_z*rho[2] + 2*beta_z_pre*beta_x_pre*a + sigma_pre^2
    d3 = beta_theta_0*beta_theta_pre*sig_theta^2 + beta_x_0*beta_x_pre*sig_x^2 + 
        beta_z_0*beta_z_pre*sig_z^2 + beta_theta_0*beta_x_pre*rho[1]*sig_theta*sig_x + 
        beta_theta_pre*beta_x_0*rho[1]*sig_theta*sig_x + beta_x_0*beta_z_pre*a + beta_x_pre*beta_z_pre*a + 
        beta_theta_0*beta_z_pre*rho[2]*sig_theta*sig_z + 
        beta_theta_pre*beta_z_0*rho[2]*sig_theta*sig_z 
    # cov matrix of the 2 pre-period outcomes
    sigma_yy = matrix(c(d, d3, d3, d2), 2)
    
    # Defining matrix to use theorem 5.1 bias expression
    B = cbind(sigma_thetax, sigma_thetay)
    D = rbind(cbind(sigma_XX, sigma_xy), cbind(t(sigma_xy), sigma_yy))
    
    b = matrix(c(mu_x_1 - mu_x_0, mu_z_1 - mu_z_0, beta_theta_0*(mu_theta_1 - mu_theta_0) + beta_x_0*(mu_x_1 - mu_x_0) + beta_z_0*(mu_z_1 - mu_z_0), beta_theta_pre*(mu_theta_1 - mu_theta_0) + beta_x_pre*(mu_x_1 - mu_x_0) + beta_z_pre*(mu_z_1 - mu_z_0)  ))
    
    final_bias = beta_theta_1*((mu_theta_1 - mu_theta_0) - B%*%solve(D)%*%b)
    
    
    ### calculating bias for just matching on X
    cov_Xtheta = matrix(c(sqrt(sig_theta^2*sig_x^2)*rho[1], sqrt(sig_theta^2*sig_z^2)*rho[2]),
                        nrow = 1)
    
    Delta_theta = beta_theta_1 - mean(c(beta_theta_0, beta_theta_pre))
    delta_theta = mu_theta_1 - mu_theta_0
    
    Delta_X = beta_x_1 - mean(c(beta_x_0, beta_x_pre))
    delta_X = mu_x_1 - mu_x_0
    
    Delta_Z = beta_z_1 - mean(c(beta_z_0, beta_z_pre))
    delta_Z = mu_z_1 - mu_z_0
    
    delta_theta_tilde = delta_theta - cov_Xtheta %*% solve(sigma_XX) %*% t(cbind(delta_X, delta_Z))
    
    bias_X = Delta_theta * delta_theta_tilde
    
    return(c(final_bias, bias_X))
}


## Calculates bias based on our estimator
bias_match_both_myestimator = function(rho, beta_theta_0, beta_x_0, beta_theta_1, beta_x_1, beta_z_1, beta_z_0,
                                       beta_theta_pre, beta_x_pre, beta_z_pre,
                                       mu_theta_1, mu_theta_0, mu_x_1, mu_x_0, mu_z_1, mu_z_0, sig_theta, 
                                       sig_x, sig_z, sigma_pre, a = 0) {
    # cov matrix of X
    sigma_XX <- matrix(c(sig_x^2, a, a, sig_z^2),
                       2)
    # cov matrix of theta and X
    sigma_thetax = matrix(c(sig_theta*sig_x*rho[1], sig_theta*sig_z*rho[2]), nrow = 1)
    
    # new variance with the correlated
    vt = sig_theta^2 - sigma_thetax%*%solve(sigma_XX)%*%t(sigma_thetax)
    
    # reliability
    reliability = (beta_theta_0^2 + beta_theta_pre^2)*vt/((beta_theta_0^2 + beta_theta_pre^2)*vt + sigma_pre^2)
    
    # new delta theta
    dx = matrix(c(mu_x_1 - mu_x_0, mu_z_1 - mu_z_0), nrow = 2)
    dt = (mu_theta_1 - mu_theta_0) - sigma_thetax%*%solve(sigma_XX)%*%dx
    
    # bias as reported in Theom 5.2
    final_bias = beta_theta_1*dt*(1 - reliability)
    
    return(final_bias)
}


### Sanity check: does our guess align with the truth when a \neq 0 

beta_theta_1 = 1.5; beta_theta_0 = 1.0; beta_theta_pre = 0.5

beta_x_1 = 1.3; beta_x_0 = 1.1; beta_x_pre = 0.6

beta_z_1 = 1.0; beta_z_0 = 0.7; beta_z_pre = 0.3

mu_theta_1 = mu_x_1 = mu_z_1 = 1
mu_theta_0 = mu_x_0 = mu_z_0 = 0
sig_z = sig_theta = sig_x = sigma_pre = 1

rho = c(0.5, 0.3)

a = 0  

truth = bias_match_both_truth(rho = rho, beta_theta_0 = beta_theta_0, beta_x_0, beta_theta_1, 
                              beta_x_1 = beta_x_1, beta_theta_pre = beta_theta_pre, beta_x_pre = beta_x_pre,
                              beta_z_pre = beta_z_pre,
                              beta_z_1 = beta_z_1, beta_z_0 = beta_z_0,
                              mu_theta_1 = mu_theta_1, mu_theta_0 = mu_theta_0, mu_x_1 = mu_x_1, mu_x_0 = mu_x_0,
                              mu_z_1 = mu_z_1, mu_z_0= mu_z_0, sig_theta = sig_theta, sig_x = sig_x, 
                              sig_z = sig_z, sigma_pre = sigma_pre, a = a)


guess = bias_match_both_myestimator(rho = rho, beta_theta_0 = beta_theta_0, beta_x_0, beta_theta_1, 
                                    beta_x_1 = beta_x_1,beta_theta_pre = beta_theta_pre, beta_x_pre = beta_x_pre,
                                    beta_z_pre = beta_z_pre,
                                    beta_z_1 = beta_z_1, beta_z_0 = beta_z_0,
                                    mu_theta_1 = mu_theta_1, mu_theta_0 = mu_theta_0, mu_x_1 = mu_x_1, 
                                    mu_x_0 = mu_x_0,
                                    mu_z_1 = mu_z_1, mu_z_0= mu_z_0, sig_theta = sig_theta, sig_x = sig_x, 
                                    sig_z = sig_z, sigma_pre = sigma_pre)

truth; guess

a = 0.5

truth = bias_match_both_truth(rho = rho, beta_theta_0 = beta_theta_0, beta_x_0, beta_theta_1, 
                              beta_x_1 = beta_x_1, beta_theta_pre = beta_theta_pre, beta_x_pre = beta_x_pre,
                              beta_z_pre = beta_z_pre,
                              beta_z_1 = beta_z_1, beta_z_0 = beta_z_0,
                              mu_theta_1 = mu_theta_1, mu_theta_0 = mu_theta_0, mu_x_1 = mu_x_1, mu_x_0 = mu_x_0,
                              mu_z_1 = mu_z_1, mu_z_0= mu_z_0, sig_theta = sig_theta, sig_x = sig_x, 
                              sig_z = sig_z, sigma_pre = sigma_pre, a = a)


guess = bias_match_both_myestimator(rho = rho, beta_theta_0 = beta_theta_0, beta_x_0, beta_theta_1, 
                                    beta_x_1 = beta_x_1,beta_theta_pre = beta_theta_pre, beta_x_pre = beta_x_pre,
                                    beta_z_pre = beta_z_pre,
                                    beta_z_1 = beta_z_1, beta_z_0 = beta_z_0,
                                    mu_theta_1 = mu_theta_1, mu_theta_0 = mu_theta_0, mu_x_1 = mu_x_1, 
                                    mu_x_0 = mu_x_0,
                                    mu_z_1 = mu_z_1, mu_z_0= mu_z_0, sig_theta = sig_theta, sig_x = sig_x, 
                                    sig_z = sig_z, sigma_pre = sigma_pre)

truth; guess
```


### Comparing above function with oracle bias calculator

```{r}
source( here::here( "oracle_bias_calculators.R" ) )

beta_theta_1 = 1.5; beta_theta_0 = 1.0; beta_theta_pre = 0.5
beta_x_1 = 1.3; beta_x_0 = 1.1; beta_x_pre = 0.6
beta_z_1 = 1.0; beta_z_0 = 0.7; beta_z_pre = -0.3
mu_theta_1 = mu_x_1 = 1
mu_z_1 = 2
mu_theta_0 = mu_x_0
mu_z_0 = -1
sig_z = 0.5
sig_theta = 0.8
sig_x = 0.7
sigma_pre = 2.1

rho = c(0.5, 0.3)
num_pre = 2
a = 0.25

truth = bias_match_both_truth(rho = rho, 
                              beta_theta_0 = beta_theta_0, beta_x_0 = beta_x_0, beta_z_0 = beta_z_0,
                              beta_theta_1 = beta_theta_1, beta_x_1 = beta_x_1, beta_z_1 = beta_z_1,
                              beta_theta_pre = beta_theta_pre, beta_x_pre = beta_x_pre, beta_z_pre = beta_z_pre,
                              mu_theta_1 = mu_theta_1, mu_theta_0 = mu_theta_0, 
                              mu_x_1 = mu_x_1, mu_x_0 = mu_x_0,
                              mu_z_1 = mu_z_1, mu_z_0= mu_z_0, 
                              sig_theta = sig_theta, sig_x = sig_x, sig_z = sig_z,
                              sigma_pre = sigma_pre, a = a)

# redefining parameters to match your inputs    
bt0 = c(beta_theta_pre, beta_theta_0)
bx0 = cbind(c(beta_x_pre, beta_x_0), c(beta_z_pre, beta_z_0))
mX1 = c(mu_x_1, mu_z_1)
mX0 = c(mu_x_0, mu_z_0)
Sigma_theta = sig_theta^2
Sigma_X = matrix( c(sig_x^2,a,a,sig_z^2), nrow=2 )
#cov_Xtheta = rho * c( sig_x, sig_z )
cov_Xtheta = c(sig_theta*sig_x*rho[1], sig_theta*sig_z*rho[2])

sigma2_e = sigma_pre^2


truth2 = calculate_truth_general(beta_theta_1 = beta_theta_1, beta_theta_0 = bt0,
                                 beta_X_1 = beta_x_1, beta_X_0 = bx0, 
                                 mu_theta_1 = mu_theta_1, mu_theta_0 = mu_theta_0,
                                 mu_X_1 = mX1, mu_X_0 = mX0, 
                                 Sigma_theta = Sigma_theta, Sigma_X = Sigma_X, cov_Xtheta = cov_Xtheta, 
                                 sigma2_e = sigma2_e,
                                 num_pre = num_pre)

## aligned?
truth
truth2

truth - rev( truth2$bias[3:4] )

```



## getting theoretical truths
```{r}

#### Actual simulation

# Number of simulation replicates per scenario
K = 10 #1000

# boundary
#sigma_pre = 1.347 (the exact decision boundary point)
beta_theta_1 = 1.5; beta_theta_0 = 1.0; beta_theta_pre = 0.5

beta_x_1 = 1.3; beta_x_0 = 1.1; beta_x_pre = 0.6

beta_z_1 = 1.0; beta_z_0 = 0.7; beta_z_pre = 0.3

mu_theta_1 = mu_x_1 = mu_z_1 = 1
mu_theta_0 = mu_x_0 = mu_z_0 = 0
sig_z = sig_theta = sig_x = 1

rho = c(0.3, 0.4)

sigma_pre_tests = c(0.3, 0.6, 0.75, 0.9, 1.0, 1.1, 1.2, 1.4, 1.5)
a = 0.3

#boundary is at sigma_pre = 1.03

### let's first calculate the theoretical biases under these scenarios
### using our formula in the paper ### (green line in Figure 3)
bias_matchX = bias_matchboth = true_diffs = vector()

for (j in 1:length(sigma_pre_tests)) {
    
    sigma_pre = sigma_pre_tests[j]
    
    truth = bias_match_both_truth(rho = rho, beta_theta_0 = beta_theta_0, beta_x_0,
                                  beta_theta_1, beta_x_1 = beta_x_1, beta_theta_pre = beta_theta_pre,
                                  beta_x_pre = beta_x_pre, beta_z_pre = beta_z_pre, beta_z_1 = beta_z_1,
                                  beta_z_0 = beta_z_0,
                                  mu_theta_1 = mu_theta_1, mu_theta_0 = mu_theta_0, 
                                  mu_x_1 = mu_x_1, mu_x_0 = mu_x_0, mu_z_1 = mu_z_1, mu_z_0= mu_z_0, 
                                  sig_theta = sig_theta, sig_x = sig_x, sig_z = sig_z, sigma_pre = sigma_pre, 
                                  a = a)
    
    bias_matchX[j] = truth[2]
    bias_matchboth[j] = truth[1]
    
}

diff = abs(bias_matchX) - abs(bias_matchboth)

diff
```

Compulsive check against oracle

```{r}
    source( here::here( "oracle_bias_calculators.R" ) )

    # redefining parameters to match inputs    
    bt0 = c(beta_theta_pre, beta_theta_0)
    bx0 = cbind(c(beta_x_pre, beta_x_0), c(beta_z_pre, beta_z_0))
    mX1 = c(mu_x_1, mu_z_1)
    mX0 = c(mu_x_0, mu_z_0)
    Sigma_theta = sig_theta^2
    Sigma_X = matrix( c(sig_x^2,a,a,sig_z^2), nrow=2 )
    cov_Xtheta = rho * c( sig_x, sig_z )
    
    ct <- calculate_truth_general( beta_theta_0 = bt0,
                      beta_X_0 = bx0,
                      beta_theta_1 = beta_theta_1, 
                      beta_X_1 = c( beta_x_1, beta_z_1 ),
                      mu_theta_1 = mu_theta_1, mu_theta_0 = mu_theta_0,
                      mu_X_1 = mX1, mu_X_0 = mX0,
                      Sigma_theta = Sigma_theta, 
                      cov_Xtheta = cov_Xtheta,
                      Sigma_X = Sigma_X, sigma2_e = sigma_pre_tests[[1]]^2, num_pre = 2 )
    ct$bias[3:4] - c( bias_matchX[[1]], bias_matchboth[[1]] )
    
    # truth_o = map_df( sigma_pre_tests, calculate_truth_general,
    #                   beta_theta_0 = c( beta_theta_pre, beta_theta_0 ), 
    #                   beta_X_0 = bx,
    #                   beta_theta_1 = beta_theta_1, 
    #                   beta_X_1 = c( beta_x_1, beta_z_1 ),
    #                   mu_theta_1 = mu_theta_1, mu_theta_0 = mu_theta_0,
    #                   mu_X_1 = c( mu_x_1, mu_z_1 ), mu_X_0 = c( mu_x_0, mu_z_0 ),
    #                   Sigma_theta = sig_theta, 
    #                   Sigma_X = Sigma_x )



```


# empirically simulating data and running our guideline

```{r}
source( here::here( "DiD_matching_func.R" ) )

N = 20000
### this is actual empirically measured ones ### (blue line in Figure 3)
correct_decision = a_tau_xy = a_est_beta0 = a_est_beta1 = a_est_delta_theta = a_est_sig_pre_sq = vector()
for (j in 1:length(sigma_pre_tests)) {
    sigma_pre= sigma_pre_tests[j]
    match = tau_xy = est_beta0 = est_beta1 = est_delta_theta = est_sig_pre_sq = vector()
    for (i in 1:K) {
        
        # using your function from data_simulator
        df = make_data(N, beta_theta_1, beta_theta_0, beta_theta_pre, 
                       beta_X_1 = beta_x_1, beta_X_0 = beta_x_0, beta_X_pre = beta_x_pre,
                       beta_Z_1 = beta_z_1, beta_Z_0 = beta_z_0, beta_Z_pre = beta_z_pre,
                       mu_theta_1, mu_theta_0, mu_X_1 = mu_x_1, mu_X_0 = mu_x_0, 
                       mu_Z_1 = mu_z_1, mu_Z_0 = mu_z_0,
                       sigma2_theta = sig_theta^2, sigma2_X = sig_x^2, sigma2_Z = sig_z^2,
                       sigma2_pre = sigma_pre^2, num_pre = 2, rho = rho, a = a, seed = i)
        
        Y_pre = colnames(df)[5:6]
        Y_post =  colnames(df)[ncol(df)]
        treatment = "treatment"
        
        # using your function from DiD_match_func
        result = DiD_matching_guideline(Y_pre, Y_post, treatment, X = c("X", "Z"), data = df)
        
        match[i] = result$result[2, 2]
        tau_xy[i] = result$result$bias_reduction[2]
        est_beta0[i] = result$delta$beta_pre[2]
        est_beta1[i] = result$delta$beta_post[2]
        est_delta_theta[i] = result$delta$delta[2]
        est_sig_pre_sq[i] = result$est_sigma2
        # print(i)
    }
    correct_decision[j] = mean(unlist(match))
    a_tau_xy[j] = mean(tau_xy)
    a_est_beta0[j] = mean(est_beta0)
    a_est_beta1[j] = mean(est_beta1)
    a_est_delta_theta[j] = mean(est_delta_theta)
    a_est_sig_pre_sq[j] = mean(est_sig_pre_sq)
    a_tau_xy[j] = mean(tau_xy)
    
    print(j)
}
```



```{r}
a_tau_xy; diff

a_est_beta0; mean(c(beta_theta_0, beta_theta_pre))
a_est_beta1; beta_theta_1
a_est_delta_theta; mu_theta_1 - mu_theta_0
a_est_sig_pre_sq; sigma_pre_tests^2

```



## plotting
```{r}
library(ggplot2); library(latex2exp); library(gridExtra); library(ggpubr)

# Figure specifications

true_diffs = diff
s = 5
w = 50
s2 = 5
a1 = 15
a2 = 20
boundary = 1.03^2
plot_df = data.frame(sigma_pre = sigma_pre_tests^2, correct_decision, a_tau_xy, true_diffs)

save(plot_df, file = "~/Downloads/plot_df")

# left panel of Figure 3
plot_1 = ggplot(data = plot_df, aes(x = sigma_pre, y = correct_decision)) + 
    geom_point(size = 2) + 
    geom_line(size = 2) + xlab(TeX("$\\sigma_{E}^2$")) + 
    ylab("Proportion Match") + 
    geom_vline(xintercept=boundary,linetype= "dotted", size = 2, col = "red") + 
    theme(axis.text=element_text(size=a1), axis.title=element_text(size=a2,face="bold"), 
          panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.background = element_blank(), axis.line = element_line(colour = "black"), 
          plot.title = element_text(size = a2, face = "bold"), axis.title.x = element_text(vjust=-0.5))

plot2_df = data.frame(sigma_pre = c(plot_df$sigma_pre, plot_df$sigma_pre),
                      difference = c(plot_df$a_tau_xy, 
                                     plot_df$true_diffs), 
                      group = factor(rep(c("Estimated Difference", "True Difference"), each = nrow(plot_df))))

# right panel of figure 3
plot_2 = ggplot(data = plot2_df, aes(x = sigma_pre, y = difference, col = group)) + 
    geom_point(size = 2) + 
    geom_line(size = 2) + xlab(TeX("$\\sigma_{E}^2$")) + 
    ylab("Bias Reduction from Matching") +
    scale_color_manual(values = c("Blue", "Dark Green")) + 
    geom_vline(xintercept=boundary,linetype= "dotted", size = 2, col = "red") +  
    theme(axis.text=element_text(size=a1), axis.title=element_text(size=a2,face="bold"), 
          panel.grid.major = element_blank(), legend.position= "top", legend.title=element_blank(),
          legend.text=element_text(size=a1), panel.grid.minor = element_blank(), 
          panel.background = element_blank(), axis.line = element_line(colour = "black"), 
          plot.title = element_text(size = a2, face = "bold"), axis.title.x = element_text(vjust=-0.5)) 

fig_3 = ggarrange(plot_1, plot_2, nrow = 1)

fig_3
```



